---
title: "2017.12 Larval survival PAR"
author: "Mikaela Nordborg"
date: "12/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Background
Analysis of data sets from A. millepora embryo experiment performed in  December 2017 to test the effects of heavy fuel oil WAF in the presence and absence of ultraviolet radiation (+UV vs -UV). All analysis performed in (at least) four steps:
    - Model fitting, evaluation and interpretation of -UV/PAR only treatment data
    - Model fitting, evaluation and interpretation of +UV treatment data
    - Extraction of no effect concentration (NEC), 10 and 50% effect or lethal concentrations (EC/LCx) and associated 95% credible intervals.
    - Comparison of posterior distributions of extracted NEC and 50% threshold concentrations for each light treatment (+/-UV).

Compromised or invalid replicates identified prior to data import into R but removal is performed after import. Please see methods of main paper and *Table ___*, Supplementary materials for further details. Control treatment (filtered seawater) set as one third of the lowest treatment concentration used in each assays to avoid potential issues with transformations after data import. Treatment concentrations log10 transformed and analysed on log-scale due to the spacing of treatment concentrations and range covered (equal to or larger than 3 orders of magnitude).


A majority of the data sets consist of binomial data and the following terms are used throughout:
    year = year and month experiment was performed
    endpoint = endpoint assessed
    factor = light treatment used
        PAR = -UV/in the absence of UV light
        UV = +UV/in the presence of UV light
    raw.x = time averaged, measured treatment concentration in μg TAH L-1
    log.x = log10-transfomred, time-averaged, treatment concentrations (measured in μg TAH L-1)
    suc = number of successes in sample (eg number of successfully settled larvae)
    tot = total number of organisms in sample
    prop = proportion of successes out of total tries/organisms in the sample
    use_in_model = Yes/No, used to filter out samples/replicates that should not be used for model fitting
    reason_for_exclusion = outlines the reason for why a sample/replicate was excluded from model fitting
    comments = if further information regarding a sample/replicate may be relevant

Embryonic survival data available for three time points: 48h, 96h and 192h. Each dataset analysed separately

Please note, where survival analyses replicates had an increased number of embryos/larvae relative to start of exposure (due to fragmentation) the suc variable was adjusted to match tot (ie 100% survival) to enable statistical analysis using a No Effect Concentration-model. Please see 'Comments' column of data sheet for details on which replicates were adjusted prior to import into R.


Analysis performed by Mikaela Nordborg.


## Packages used and installation of latest version of jagsNEC

Analysis performed using package jagsNEC and it's dependencies. The latest version of jagsNEC installed prior to start of analysis (20 July 2020).

```{r}
#devtools::install_github("AIMS/NEC-estimation")
library(jagsNEC)
library(R2jags)
require(tidyverse)
library(beepr)
```



## Embryonic survival 

### 48h

#### Import data, check data type and perform data preparation if required

Import data
```{r}
data.E.surv48.Dec.raw <- read_csv("Data/2017.12_HFO_embryo_surv_48h.csv")
str(data.E.surv48.Dec.raw)
head(data.E.surv48.Dec.raw)
```

Initial data wrangling
```{r}
data.E.surv48.Dec.raw <- as.data.frame(data.E.surv48.Dec.raw)
data.E.surv48.Dec.raw$raw.x <- as.numeric(as.character(data.E.surv48.Dec.raw$raw.x))
str(data.E.surv48.Dec.raw)
data.E.surv48.Dec.raw$suc <- as.integer(data.E.surv48.Dec.raw$suc)
data.E.surv48.Dec.raw$tot <- as.integer(data.E.surv48.Dec.raw$tot)
str(data.E.surv48.Dec.raw)
data.E.surv48.Dec.raw$prop <- as.numeric(as.character(data.E.surv48.Dec.raw$prop))
str(data.E.surv48.Dec.raw)
head(data.E.surv48.Dec.raw)
tail(data.E.surv48.Dec.raw)
```


Add a small value (1 order of magnitude less than the lowest treatment concentrations used) to raw.x for 0 ug/L replicates (filtered seawater control) to avoid issues with transformations
```{r}
data.E.surv48.Dec.raw <- data.E.surv48.Dec.raw %>%
                            mutate(raw.x=ifelse(raw.x==0, 0.3, data.E.surv48.Dec.raw$raw.x))
head(data.E.surv48.Dec.raw)
tail(data.E.surv48.Dec.raw)
```


Add a log.x variable
```{r}
data.E.surv48.Dec.raw <- mutate(data.E.surv48.Dec.raw, log.x = log10(data.E.surv48.Dec.raw$raw.x))
str(data.E.surv48.Dec.raw)
head(data.E.surv48.Dec.raw)
```


Filter according to light treatment
```{r}
data.E.surv48.PAR.raw <- filter(data.E.surv48.Dec.raw, factor=="PAR")
save(data.E.surv48.PAR.raw, file = "data.E.surv48.PAR.raw.RData")
data.E.surv48.UV.raw <- filter(data.E.surv48.Dec.raw, factor=="UV")
save(data.E.surv48.UV.raw, file = "data.E.surv48.UV.raw.RData")
```


Filter according to whether replicates are to be included when fitting models or not
```{r}
data.E.surv48.PAR <- filter(data.E.surv48.PAR.raw, use_in_model=="Yes")
data.E.surv48.UV <- filter(data.E.surv48.UV.raw, use_in_model=="Yes")
```


#### -UV/PAR


##### Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
unique(data.E.surv48.PAR$raw.x)
par(mfrow=c(2,1))
hist(data.E.surv48.PAR$raw.x)
hist(data.E.surv48.PAR$suc/data.E.surv48.PAR$tot)
```


###### Fit models

```{r}
out.E.surv48.PAR.all <- fit.jagsMANEC(data = data.E.surv48.PAR, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 10000)
beep("mario")
save(out.E.surv48.PAR.all, file = "2017.12_Esurv48PAR_modfit1.RData")
load("2017.12_Esurv48PAR_modfit1.RData")
```

```{r}
check.chains(out.E.surv48.PAR.all)
```

Evidence of poor chain mixing observed for:
    - ECxWeibull2 (top, beta & bot)
    - ECxWeibull1 (top, beta & bot)
    - NECsigmoidal (beta)
    - NEC4param (beta)
    - NEC3param (beta)


Evidence of poor convergence or autocorrelation observed for:
    - ECx4param
    - ECxExp
    


Re-fit using a longer burn-in and higher iterations
```{r}
out.E.surv48.PAR.all <- fit.jagsMANEC(data = data.E.surv48.PAR, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 20000)
beep("mario")
save(out.E.surv48.PAR.all, file = "2017.12_Esurv48PAR_modfit2.RData")
load("2017.12_Esurv48PAR_modfit2.RData")
```

```{r}
check.chains(out.E.surv48.PAR.all)
```

Evidence of poor fit/that model is inappropriate for all models except for:
    - ECxLinear
    - NEC3param (only beta showing indications of poor mixing)
    - NEC4param (only beta showing indications of poor mixing)
    - NECsigmoidal (only beta showing indications of poor mixing)
    
    


Check if model median, credible intervals and NEC estimate are reasonable compared to the raw data
```{r}
plot(out.E.surv48.PAR.all, all_models = TRUE, add.NEC = TRUE)
```

    

```{r}
plot(out.E.surv48.PAR.all, add.EC10 = FALSE, add.NEC = FALSE)
```


Drop inappropriate models and models with non-convergence
```{r}
out.E.surv48.PAR.mod <- modify_jagsMANEC(out.E.surv48.PAR.all, drop.models = c( "NECHormesis", "NECsigmoidal", "ECxExp", "ECxsigmoidal", "ECx4param", "ECxWeibull1", "ECxWeibull2"))
```

```{r}
plot(out.E.surv48.PAR.mod, add.EC10 = FALSE, add.NEC = FALSE)
```

```{r}
plot(out.E.surv48.PAR.mod, all_models = TRUE, add.NEC = TRUE)
```


Check for evidence of overdispersion for remaining models
```{r}
out.E.surv48.PAR.mod$mod.stats
```

All models show some degree of overdispersion but no individual overdispersion parameterswere >0.87.


Re-fit MANEC with over.disp = TRUE
```{r}
out.E.surv48.PAR.all.od <- fit.jagsMANEC(data = data.E.surv48.PAR, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 20000,
                        over.disp = TRUE)
beep("mario")
save(out.E.surv48.PAR.all.od, file = "2017.12_Esurv48PAR_modfit3.RData")
load("2017.12_Esurv48PAR_modfit3.RData")
```

```{r}
check.chains(out.E.surv48.PAR.all.od)
```

All models showing strong indications of poor chain mixing, autocorrelation or non-convergence except for:
    - NEC3param (only poor mixing for beta)
    - NECHormesis (only poor mixing for beta)
    - NECsigmoidal (only poor mixing for beta)
    - ECxLinear
    
  
Check if model median, credible intervals and NEC estimates are reasonable compared to the raw data
```{r}
plot(out.E.surv48.PAR.all.od, all_models = TRUE, add.NEC = TRUE)
```

Based on graphical evaluation of model fit the following models should be excluded:
    - NECHormesis
    
    
Drop poor model fits and models with convergence or autocorrelation issues
```{r}
out.E.surv48.PAR.mod.od <- modify_jagsMANEC(out.E.surv48.PAR.all.od, drop.models = c("NEC4param", "NECHormesis", "NECsigmoidal", "ECxExp", "ECxsigmoidal", "ECx4param", "ECxWeibull1", "ECxWeibull2"))
```

```{r}
plot(out.E.surv48.PAR.mod.od, all_models = TRUE, add.NEC = FALSE)
```


```{r}
plot(out.E.surv48.PAR.mod.od, add.EC10 = FALSE, add.NEC = FALSE)
```

Compare to MANEC fitted using the binomial distribution
```{r}
plot(out.E.surv48.PAR.mod, add.EC10 = FALSE, add.NEC = FALSE)
```


Both MANECs fitted are, overall, a poor fit to the observed data with no possibility of extracting threhsold concentrations. However, both indicate a slight trend of decreasing survival with increasing treatment concentration. 



Rename model output for selected model
```{r}
out.E.surv48.PAR <- out.E.surv48.PAR.mod
```


```{r}
out.E.surv48.PAR.NEC <- modify_jagsMANEC(out.E.surv48.PAR, drop.models = "ECxLinear")
```

```{r}
plot(out.E.surv48.PAR.NEC)
```




Save the output for the selected model
```{r}
save(out.E.surv48.PAR, file = "2017.12_Esurv48PAR_modfit.RData")
load("2017.12_Esurv48PAR_modfit.RData")
```


```{r}
save(out.E.surv48.PAR.NEC, file = "2017.12_Esurv48PAR_modfitNEC.RData")
load("2017.12_Esurv48PAR_modfitNEC.RData")
```



##### Extract results


Extract LC10 and LC50 (with 95% credible intervals) from posterior and backtransform if required

```{r}
LC10.E.surv48.PAR <- extract_ECx(out.E.surv48.PAR, ECx.val = 10, type = "absolute")
LC10.E.surv48.PAR <- 10^LC10.E.surv48.PAR
LC10.E.surv48.PAR
```

```{r}
LC50.E.surv48.PAR <- extract_ECx(out.E.surv48.PAR, ECx.val = 50, type = "absolute")
LC50.E.surv48.PAR <- 10^LC50.E.surv48.PAR
LC50.E.surv48.PAR
```

No LC10 or LC50 reported in results section as all three threshold concentrations are higher than the highest treatment used in assay. 



Extract complete posteriors for use in plotting and comparisons between light treatments
```{r}
pred.E.surv48.PAR <- out.E.surv48.PAR$pred.vals
str(pred.E.surv48.PAR)
save(pred.E.surv48.PAR, file = "2017.12_Efertsurv48PAR_predvals.RData")
```

```{r}
pred.E.surv48.PAR.NEC <- out.E.surv48.PAR.NEC$pred.vals
str(pred.E.surv48.PAR.NEC)
save(pred.E.surv48.PAR.NEC, file = "2017.12_Efertsurv48PAR_predvalsNEC.RData")
```


#### +UV/UV


##### Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
unique(data.E.surv48.UV$raw.x)
par(mfrow=c(2,1))
hist(data.E.surv48.UV$raw.x)
hist(data.E.surv48.UV$suc/data.E.surv48.UV$tot)
```



##### Fit models

Fit a model-averaged NEC model


```{r}
out.E.surv48.UV.all <- fit.jagsMANEC(data = data.E.surv48.UV, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 10000)
save(out.E.surv48.UV.all, file = "2017.12_Esurv48UV_modfits1.RData")
load("2017.12_Esurv48UV_modfits1.RData")
beep("mario")
```


Check chain mixing and aurocorrelation for each model fit
```{r}
check.chains(out.E.surv48.UV.all)
```

Poor chain mixing and autocorrelation observed for several of the models fitted. 



Re-fit with higher burn-in and iterations
```{r}
out.E.surv48.UV.all <- fit.jagsMANEC(data = data.E.surv48.UV, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 20000)
save(out.E.surv48.UV.all, file = "2017.12_Esurv48UV_modfits2.RData")
load("2017.12_Esurv48UV_modfits2.RData")
beep("mario")
```

```{r}
check.chains(out.E.surv48.UV.all)
```

Minor indications of poor chain mixing or autocorrelation observed for:
    - ECxWeibull2 (top & beta)
    - ECxWeibull1 (bot & EC50)
    - ECx4param (bot & EC50)
    - NEC4param (beta & SSsim)
    
    
Non-convergence observed for:
    - NECsigmoidal
    


```{r}
plot(out.E.surv48.UV.all, add.EC10 = TRUE, add.NEC = FALSE)
```

MANEC fit strongly driven by models with a relative bottom asymptote. This is unlikely to be appropriate for this data set as survival would, most likely, continue to decrease if higher treatment concentrations were achieved. 



Check if model median, credible intervals and NEC estimates are reasonable compared to the raw data for individual candidate models
```{r}
plot(out.E.surv48.UV.all, all_models = TRUE, add.NEC = TRUE)
```
Based on graphical evaluation of model fit, in particular positioning of bottom asymptotes, all models except the following should be excluded:
    - NEC3param

    


Remove models where chains did not converge or that do not make sense graphically
```{r}
out.E.surv48.UV.mod <- modify_jagsMANEC(out.E.surv48.UV.all, drop.models = c("NEC4param", "NECsigmoidal", "ECxLinear", "ECxExp", "ECx4param", "ECxWeibull1", "ECxWeibull2"))
```

```{r}
plot(out.E.surv48.UV.mod, add.NEC = TRUE, add.EC10 = TRUE)
```



Check for evidence of overdispersion
```{r}
out.E.surv48.UV.mod$mod.stats
```

Overdispersion parameter = 0.89


Fit a MANEC with over.disp=TRUE
```{r}
out.E.surv48.UV.all.od <- fit.jagsMANEC(data = data.E.surv48.UV, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 20000,
                        over.disp = TRUE)
save(out.E.surv48.UV.all.od, file = "2017.12_Esurv48UV_modfits3.RData")
load("2017.12_Esurv48UV_modfits3.RData")
beep("mario")
```


```{r}
check.chains(out.E.surv48.UV.all.od)
```

All models show some degree of poor chain mixing, autocorrelation or non-convergence except:
    - ECxLinear


```{r}
plot(out.E.surv48.UV.all.od, all_models = TRUE, add.NEC = TRUE)
```

Based on graphical evaluation of model fit all models except the following should be excluded:
    - NEC3param
    - NECHormesis


```{r}
out.E.surv48.UV.mod.od <- modify_jagsMANEC(out.E.surv48.UV.all.od, drop.models = c("NEC4param", "NECsigmoidal", "ECxLinear", "ECxExp", "ECx4param", "ECxWeibull1", "ECxWeibull2"))
```

```{r}
plot(out.E.surv48.UV.mod.od, all_models = TRUE, add.NEC = TRUE)
```


```{r}
plot(out.E.surv48.UV.mod.od, add.NEC = TRUE, add.EC10 = TRUE)
```

Compare to MANEC fitted using the binomial distribution
```{r}
plot(out.E.surv48.UV.mod, add.NEC = TRUE, add.EC10 = TRUE)
```

As model diagnostics were better for the MANEC fitted on the binomial distribution (only NEC3param model used) this was used in extraction and interpretation of results.


Rename model output for selected model
```{r}
out.E.surv48.UV <- out.E.surv48.UV.mod
```




Save the output for the selected model
```{r}
save(out.E.surv48.UV, file = "2017.12_Esurv48UV_modfit.RData")
load("2017.12_Esurv48UV_modfit.RData")
```





##### Extract results

Extract NEC, LC10 and LC50 (with 95% credible intervals) from posterior and backtransform if required


```{r}
NEC.E.surv48.UV <- out.E.surv48.UV$NEC
NEC.E.surv48.UV <- 10^NEC.E.surv48.UV
NEC.E.surv48.UV
```


```{r}
LC10.E.surv48.UV <- extract_ECx(out.E.surv48.UV, ECx.val = 10, type = "absolute")
LC10.E.surv48.UV <- 10^LC10.E.surv48.UV
LC10.E.surv48.UV
```


```{r}
LC50.E.surv48.UV <- extract_ECx(out.E.surv48.UV, ECx.val = 50, type = "absolute")
LC50.E.surv48.UV <- 10^LC50.E.surv48.UV
LC50.E.surv48.UV
```



Extract complete posteriors for use in plotting and model comparison
```{r}
pred.E.surv48.UV <- out.E.surv48.UV$pred.vals
str(pred.E.surv48.UV)
save(pred.E.surv48.UV, file = "2017.12_Efertsurv48UV_predvals.RData")
```



#### PLot results

```{r}
library(ggplot2)
library(scales)
```



##### Combined "all models subset" plot

```{r}
p0= ggplot()
p0= p0+ scale_color_manual(values = c("UV" = "steelblue", "PAR" = "seagreen")) + theme_light()
#Add 95% credible intervals
p0= p0+  geom_ribbon(aes(x=10^pred.E.surv48.PAR$x, ymin=pred.E.surv48.PAR$lw, ymax=pred.E.surv48.PAR$up, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
p0= p0+  geom_ribbon(aes(x=10^pred.E.surv48.UV$x, ymin=pred.E.surv48.UV$lw, ymax=pred.E.surv48.UV$up,fill="steelblue",  alpha=0.3))
#Add model medians
p0= p0+ geom_line(aes(x=10^pred.E.surv48.PAR$x, y=pred.E.surv48.PAR$y), color = 'grey30', size=0.5)
p0= p0+ geom_line(aes(x=10^pred.E.surv48.UV$x, y=pred.E.surv48.UV$y), color = 'grey30', size=0.5)
#Add raw data points
p0= p0+ geom_point(data = data.E.surv48.PAR.raw, aes(x = raw.x, y = prop, colour=factor(factor), alpha = 0.3), size = data.E.surv48.PAR.raw$tot*0.2, position=position_jitter(width = .025, height=0.03))
p0= p0+ geom_point(data = data.E.surv48.UV.raw, aes(x = raw.x, y = prop, colour=factor(factor), alpha = 0.3), size = data.E.surv48.UV.raw$tot*0.2, position=position_jitter(width = .025, height=0.03))
#Adjust labels, axes, etc
p0 = p0+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Embryo~48~h~survival~("%")),
              subtitle = "a)")
p0= p0+ scale_y_continuous( limits = c(-0.0625, 1.25), breaks = c(0, 0.25, 0.5, 0.75, 1.0, 1.25), labels = c(0, 25, 50, 75, 100, 125)) 
p0= p0+ scale_x_continuous(limits = c(0.28, 1000), trans="log10", breaks = c(0.3, 1, 10, 100, 1000), labels = c(0, 1, 10, 100, 1000))
p0= p0+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p0= p0+ scale_fill_manual(values = c("seagreen", "steelblue"))
p0= p0+ theme(legend.position="none")
# p0 = p0  + theme(legend.position = c(0.9, 0.9))
#p0= p0+ facet_wrap(~factor, nrow = 1)
p0
```

```{r}
Esurv48ModfitplotDec <- p0
save(Esurv48ModfitplotDec, file = "2017.12_Esurv48modfitplot.RData")
```


```{r}
p0= ggplot()
p0= p0+ scale_color_manual(values = c("UV" = "steelblue", "PAR" = "seagreen")) + theme_light()
#Add 95% credible intervals
p0= p0+  geom_ribbon(aes(x=10^pred.E.surv48.PAR.NEC$x, ymin=pred.E.surv48.PAR.NEC$lw, ymax=pred.E.surv48.PAR.NEC$up, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
p0= p0+  geom_ribbon(aes(x=10^pred.E.surv48.UV$x, ymin=pred.E.surv48.UV$lw, ymax=pred.E.surv48.UV$up,fill="steelblue",  alpha=0.3))
#Add model medians
p0= p0+ geom_line(aes(x=10^pred.E.surv48.PAR.NEC$x, y=pred.E.surv48.PAR.NEC$y), color = 'grey30', size=0.5)
p0= p0+ geom_line(aes(x=10^pred.E.surv48.UV$x, y=pred.E.surv48.UV$y), color = 'grey30', size=0.5)
#Add raw data points
p0= p0+ geom_point(data = data.E.surv48.PAR.raw, aes(x = raw.x, y = prop, colour=factor(factor), alpha = 0.3), size = data.E.surv48.PAR.raw$tot*0.2, position=position_jitter(width = .025, height=0.03))
p0= p0+ geom_point(data = data.E.surv48.UV.raw, aes(x = raw.x, y = prop, colour=factor(factor), alpha = 0.3), size = data.E.surv48.UV.raw$tot*0.2, position=position_jitter(width = .025, height=0.03))
#Adjust labels, axes, etc
p0 = p0+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Embryo~48~h~survival~("%")),
              subtitle = "a)")
p0= p0+ scale_y_continuous( limits = c(-0.0625, 1.25), breaks = c(0, 0.25, 0.5, 0.75, 1.0, 1.25), labels = c(0, 25, 50, 75, 100, 125)) 
p0= p0+ scale_x_continuous(limits = c(0.28, 1000), trans="log10", breaks = c(0.3, 1, 10, 100, 1000), labels = c(0, 1, 10, 100, 1000))
p0= p0+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p0= p0+ scale_fill_manual(values = c("seagreen", "steelblue"))
p0= p0+ theme(legend.position="none")
# p0 = p0  + theme(legend.position = c(0.9, 0.9))
#p0= p0+ facet_wrap(~factor, nrow = 1)
p0
```

```{r}
Esurv48ModfitNECplot <- p0
save(Esurv48ModfitNECplot, file = "2017.12_Esurv48modfitplotNEC.RData")
```


#### Compare +/-UV posteriors

Ensure dependency packages are loaded
```{r}
library(dplyr)
library(tidybayes)
library(jagsNEC) #for manual function use
library(R2jags) #for manual function use
library(ggplot2)
```


##### NEC

Perform comparison of posterior distributions for survival NEC
```{r}
comp.E.surv48.NEC <- compare_posterior(out.E.surv48.PAR.NEC, out.E.surv48.UV, comparison = "NEC") #1st model=blue, 2nd model=orange; #place PAR model first and UV model second for colour matching in custom plots
comp.E.surv48.NEC
```

Filter posterior density based on light treatment
```{r}
comp.E.surv48.NEC.PAR <- filter(comp.E.surv48.NEC$df3.s, curve=="blue")
comp.E.surv48.NEC.UV <- filter(comp.E.surv48.NEC$df3.s, curve=="orange")
```




For custom plotting of survival NEC comparison
```{r}
p1 = ggplot(comp.E.surv48.NEC.UV, aes(x=PS))+geom_density(aes(group=curve, color =curve , fill=curve), alpha=0.4) #df3.s is an object returned by compare_posterior()
p1 = p1 + stat_pointinterval(data=comp.E.surv48.NEC.UV$df3.s, aes(y = 0.00, x = PS, group=curve),.width = c(.66, .95), size=0.5)+
  theme_light()
p1 = p1+scale_fill_manual( values = c("steelblue"))+
  scale_color_manual( values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p1 = p1 + scale_y_continuous(limits = c(-0.5, 10), breaks = c(0, 2, 4, 6, 8, 10), labels = c(0, 2, 4, 6, 8, 10), name ="Posterior probability density") 
p1 = p1 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p1 = p1 + scale_x_continuous(limits = c(-0.6, 3.3), breaks = c(0, 1, 2, 3), labels = c(1, 10, 100, 1000))
p1 = p1 + labs(x=expression(), 
               subtitle = "b)") #NEC~(μg~TAH~"L"^{-1})
p1= p1+ annotate("text", label = expression(Probability~of~NEC~difference), x = 0.55, y = 8.5, size = 2.8, colour = "grey20") #0.85 of the max y-axis limit
p1= p1+ annotate("text", label = "UV < PAR = 49%", x = 0.55, y = 7.7, size = 2.4, colour = "grey20") #0.906 of first annotation
p1
```

Rename and save plot
```{r}
Esurv48NECcompDec <- p1
save(Esurv48NECcompDec, file = "2017.12_Esurv48NECcomp.RData")
```



For custom plotting of NEC differences posterior density
```{r}
p2 = ggplot(comp.E.surv48.NEC$df4.s, aes(x=comp.E.surv48.NEC$df4.s$diff))+geom_density(aes(x=comp.E.surv48.NEC$df4.s$diff, fill = 'grey'), alpha=0.4)+ #df4.s is an object returned by compare_posterior()
  stat_pointinterval(aes(y = 0.00, x = comp.E.surv48.NEC$df4.s$diff),.width = c(.66, .95))+
   geom_vline(xintercept = 0, color = "red", lty = 2)+ theme_light()
p2 = p2+scale_fill_manual( values = c("grey", "grey"))+
  scale_color_manual( values = c("grey","grey", "steelblue1","steelblue4", "grey","grey", "grey","grey"))+theme(legend.position="none")
p2 = p2 + scale_y_continuous(name ="Differences posterior density") 
p2 = p2 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p2 = p2 + scale_x_continuous(name ="Standardized effect size") 
p2
#save(p2, file = "2017.12_LsurvNECdiff.RData")
```



### Create layouts and export

```{r}
#devtools::install_github("kassambara/ggpubr")
library(ggpubr)
```


Create layout

Load graphics
```{r}
load("2017.12_Esurv48modfitplot.RData") #Esurv48ModfitplotDec

load("2017.12_Esurv48modfitplotNEC.RData") #Esurv48ModfitNECplot
load("2017.12_Esurv48NECcomp.RData") #Esurv48NECcompDec
```


```{r}
layout.E.surv <- ggarrange(Esurv48ModfitplotDec, Esurv48NECcompDec, Esurv48ModfitNECplot, Esurv48NECcompDec,
          ncol = 2, nrow = 2,
          widths = c(0.5, 0.5))
layout.E.surv
```




Export layout
```{r}
pdf("test2.pdf", width = 8.27, height = 4.92) #height and width in inches
layout.E.surv
dev.off()
```



