---
title: "2017.12 Larval survival Dark"
author: "Mikaela Nordborg"
date: "12/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Background
Analysis of data sets from A. millepora fertilisation rate experiment performed in  December 2017, November 2019 and both November and December 2019 to test the effects of heavy fuel oil WAF in the presence and absence of ultraviolet radiation (+UV vs -UV). All analysis performed in (at least) four steps:
    - Model fitting, evaluation and interpretation of -UV/Dark only treatment data
    - Model fitting, evaluation and interpretation of +UV treatment data
    - Extraction of no effect concentration (NEC), 10 and 50% effect or lethal concentrations (EC/LCx) and associated 95% credible intervals.
    - ComDarkison of posterior distributions of extracted NEC and 50% threshold concentrations for each light treatment (+/-UV).

Compromised or invalid replicates identified prior to data import into R but removal is performed after import. Please see methods of main paper and *Table ___*, Supplementary materials for further details. Control treatment (filtered seawater) generally set as one third of the lowest treatment concentration used in each assays to avoid potential issues with transformations after data import. Treatment concentrations log10 transformed and analysed on log-scale due to the spacing of treatment concentrations and range covered (equal to or larger than 3 orders of magnitude).


A majority of the data sets consist of binomial data and the following terms are used throughout:
    year = year and month experiment was performed
    endpoint = endpoint assessed
    factor = light treatment used
        Dark = exposure performed in the absence of light
	      PAR = exposure performed under visible light -UV/in the absence of ultraviolet light
	      UV = exposure performed under visible light +UV/in the presence of ultraviolet light
    raw.x = time averaged, measured treatment concentration in μg TAH L-1
    log.x = log10-transformed, time-averaged, treatment concentrations (measured in μg TAH L-1)
    suc = number of successes in sample (eg number of successfully settled larvae)
    tot = total number of organisms in sample
    prop = proportion of successes out of total tries/organisms in the sample
    use_in_model = Yes/No, used to filter out samples/replicates that should not be used for model fitting
    reason_for_exclusion = outlines the reason for why a sample/replicate was excluded from model fitting
    comments = if further information regarding a sample/replicate may be relevant

Fertilisation rate data available across several spawning events from 2017-2019. Each dataset analysed separately




Analysis performed by Mikaela Nordborg.


## Packages used and installation of latest version of jagsNEC

Analysis performed using package jagsNEC and it's dependencies. The latest version of jagsNEC installed prior to start of analysis (20 July 2020).

```{r}
#devtools::install_github("AIMS/NEC-estimation")
library(jagsNEC)
library(R2jags)
require(tidyverse)
library(beepr)
```



## Fertilisation rate 

### December 2019

#### Import data, check data type and perform data preparation if required

Import data
```{r}
data.2019D.G.fert.raw <- read_csv("Data/2019.12_HFO_gamete_fert.csv")
str(data.2019D.G.fert.raw)
head(data.2019D.G.fert.raw)
```

Initial data wrangling
```{r}
data.2019D.G.fert.raw <- as.data.frame(data.2019D.G.fert.raw)
data.2019D.G.fert.raw$raw.x <- as.numeric(as.character(data.2019D.G.fert.raw$raw.x))
str(data.2019D.G.fert.raw)
data.2019D.G.fert.raw$suc <- as.integer(data.2019D.G.fert.raw$suc)
data.2019D.G.fert.raw$tot <- as.integer(data.2019D.G.fert.raw$tot)
str(data.2019D.G.fert.raw)
data.2019D.G.fert.raw$prop <- as.numeric(as.character(data.2019D.G.fert.raw$prop))
str(data.2019D.G.fert.raw)
head(data.2019D.G.fert.raw)
tail(data.2019D.G.fert.raw)
```


Check what treatment concentrations were used 
```{r}
unique(data.2019D.G.fert.raw$raw.x)
```

Add a small value (at least ~1 order of magnitude less than the lowest treatment concentrations used) to raw.x for 0 ug/L replicates (filtered seawater control) to avoid issues with transformations
```{r}
data.2019D.G.fert.raw <- data.2019D.G.fert.raw %>%
                            mutate(raw.x=ifelse(raw.x==0, 0.02, data.2019D.G.fert.raw$raw.x))
head(data.2019D.G.fert.raw)
tail(data.2019D.G.fert.raw)
```


Add a log.x variable
```{r}
data.2019D.G.fert.raw <- mutate(data.2019D.G.fert.raw, log.x = log10(data.2019D.G.fert.raw$raw.x))
str(data.2019D.G.fert.raw)
head(data.2019D.G.fert.raw)
```


Filter according to light treatment
```{r}
data.2019D.G.fert.Dark.raw <- filter(data.2019D.G.fert.raw, factor=="Dark")
save(data.2019D.G.fert.Dark.raw, file = "2019.12_data.G.fert.Dark.raw.RData")
data.2019D.G.fert.PAR.raw <- filter(data.2019D.G.fert.raw, factor=="PAR")
save(data.2019D.G.fert.PAR.raw, file = "2019.12_data.G.fert.PAR.raw.RData")
data.2019D.G.fert.UV.raw <- filter(data.2019D.G.fert.raw, factor=="UV")
save(data.2019D.G.fert.UV.raw, file = "2019.12_data.G.fert.UV.raw.RData")
```


Filter according to whether replicates are to be included when fitting models or not
```{r}
data.2019D.G.fert.Dark <- filter(data.2019D.G.fert.Dark.raw, use_in_model=="Yes")
data.2019D.G.fert.PAR <- filter(data.2019D.G.fert.PAR.raw, use_in_model=="Yes")
data.2019D.G.fert.UV <- filter(data.2019D.G.fert.UV.raw, use_in_model=="Yes")
```


#### Dark


##### Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
unique(data.2019D.G.fert.Dark$raw.x)
par(mfrow=c(2,1))
hist(data.2019D.G.fert.Dark$raw.x)
hist(data.2019D.G.fert.Dark$suc/data.2019D.G.fert.Dark$tot)
```


###### Fit models

```{r}
out.2019D.G.fert.Dark.all <- fit.jagsMANEC(data = data.2019D.G.fert.Dark, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 10000)
beep("mario")
save(out.2019D.G.fert.Dark.all, file = "2019.12_GfertDark_modfit1.RData")
load("2019.12_GfertDark_modfit1.RData")
```


```{r}
check.chains(out.2019D.G.fert.Dark.all)
```

Some evidence of poor chain mixing or autocorrelation for several models. 



Re-fit using higher burn-in and iterations
```{r}
out.2019D.G.fert.Dark.all <- fit.jagsMANEC(data = data.2019D.G.fert.Dark, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 20000)
beep("mario")
save(out.2019D.G.fert.Dark.all, file = "2019.12_GfertDark_modfit2.RData")
load("2019.12_GfertDark_modfit2.RData")
```


```{r}
check.chains(out.2019D.G.fert.Dark.all)
```

Minor indications of poor chain mixing or autocorrelation observed for:
    - ECxWeibull2 (beta)
    - NEC4param (beta)
    
Evidence of poor chain mixing or autocorrelation observed for:
    - ECxWeibull1 (beta, bot & EC50)
    - ECx4param (beta & EC50)
    
Non-convergence observed for:
    - NECsigmoidal


Check if model median, credible intervals and NEC estimate are reasonable compared to the raw data
```{r}
plot(out.2019D.G.fert.Dark.all, all_models = TRUE, add.NEC = TRUE)
```
Based on graphical evaluation of model fit the following should be excluded:
    - ECxLinear
    

```{r}
plot(out.2019D.G.fert.Dark.all, add.EC10 = FALSE, add.NEC = FALSE)
```


Drop inappropriate models and models with non-convergence
```{r}
out.2019D.G.fert.Dark.mod <- modify_jagsMANEC(out.2019D.G.fert.Dark.all, drop.models = c("NECsigmoidal", "ECxLinear", "ECx4param"))
```

```{r}
plot(out.2019D.G.fert.Dark.mod, add.EC10 = FALSE, add.NEC = FALSE)
```

```{r}
plot(out.2019D.G.fert.Dark.mod, all_models = TRUE, add.NEC = TRUE)
```


Check for evidence of overdispersion for remaining models
```{r}
out.2019D.G.fert.Dark.mod$mod.stats
```

All candidate models had overdispersion parameters = 1.




Re-fit MANEC with over.disp = TRUE
```{r}
out.2019D.G.fert.Dark.all.od <- fit.jagsMANEC(data = data.2019D.G.fert.Dark, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 20000,
                        over.disp = TRUE)
beep("mario")
save(out.2019D.G.fert.Dark.all.od, file = "2019.12_GfertDark_modfit3.RData")
load("2019.12_GfertDark_modfit3.RData")
```

```{r}
check.chains(out.2019D.G.fert.Dark.all.od)
```


Evidence of poor chain mixing and autocorrelation observed for:
    - NECHormesis


Non-convergence observed for:
    - ECxWeibull2
    - ECxWeibull1
    - ECx4param
    - NECsigmoidal
    - NEC4param
    - NEC3param
    
    
  
Check if model median, credible intervals and NEC estimates are reasonable compared to the raw data
```{r}
plot(out.2019D.G.fert.Dark.all.od, all_models = TRUE, add.NEC = TRUE)
```

Based on graphical evaluation of model fit the following models should be excluded:
    - ECxLinear
    - ECxWeibull2
    
    
Drop poor model fits and models with convergence or strong autocorrelation issues
```{r}
out.2019D.G.fert.Dark.mod.od <- modify_jagsMANEC(out.2019D.G.fert.Dark.all.od, drop.models = c("NEC3param", "NEC4param", "NECsigmoidal", "ECxLinear", "ECx4param", "ECxWeibull1", "ECxWeibull2"))
```

```{r}
plot(out.2019D.G.fert.Dark.mod.od, all_models = TRUE, add.NEC = FALSE)
```


```{r}
plot(out.2019D.G.fert.Dark.mod.od, add.EC10 = FALSE, add.NEC = FALSE)
```

Compare to MANEC fitted using the binomial distribution
```{r}
plot(out.2019D.G.fert.Dark.mod, add.EC10 = FALSE, add.NEC = FALSE)
```



Rename model output for selected model
```{r}
out.2019D.G.fert.Dark <- out.2019D.G.fert.Dark.mod.od
```






Save the output for the selected model
```{r}
save(out.2019D.G.fert.Dark, file = "2019.12_GfertDark_modfit.RData")
load("2019.12_GfertDark_modfit.RData")
```




##### Extract results


Extract NEC, EC10 and EC50 (with 95% credible intervals) from posterior and backtransform if required

```{r}
NEC.2019D.G.fert.Dark <- out.2019D.G.fert.Dark$NEC
NEC.2019D.G.fert.Dark <- 10^NEC.2019D.G.fert.Dark
NEC.2019D.G.fert.Dark
```


```{r}
EC10.2019D.G.fert.Dark <- extract_ECx(out.2019D.G.fert.Dark, ECx.val = 10, type = "absolute")
EC10.2019D.G.fert.Dark <- 10^EC10.2019D.G.fert.Dark
EC10.2019D.G.fert.Dark
```

```{r}
EC50.2019D.G.fert.Dark <- extract_ECx(out.2019D.G.fert.Dark, ECx.val = 50, type = "absolute")
EC50.2019D.G.fert.Dark <- 10^EC50.2019D.G.fert.Dark
EC50.2019D.G.fert.Dark
```





Extract complete posteriors for use in plotting and comparisons between light treatments
```{r}
pred.2019D.G.fert.Dark <- out.2019D.G.fert.Dark$pred.vals
str(pred.2019D.G.fert.Dark)
save(pred.2019D.G.fert.Dark, file = "2019.12_GfertDark_predvals.RData")
load("2019.12_GfertDark_predvals.RData")
```

```{r}
pred.2019D.G.fert.Dark.NEC <- out.2019D.G.fert.Dark$pred.vals
str(pred.2019D.G.fert.Dark.NEC)
save(pred.2019D.G.fert.Dark.NEC, file = "2019.12_GfertDarkNEC_predvals.RData")
load("2019.12_GfertDarkNEC_predvals.RData")
```



#### PAR/-UV

##### Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
unique(data.2019D.G.fert.PAR$raw.x)
par(mfrow=c(2,1))
hist(data.2019D.G.fert.PAR$raw.x)
hist(data.2019D.G.fert.PAR$suc/data.2019D.G.fert.PAR$tot)
```


###### Fit models

```{r}
out.2019D.G.fert.PAR.all <- fit.jagsMANEC(data = data.2019D.G.fert.PAR, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 10000)
beep("mario")
save(out.2019D.G.fert.PAR.all, file = "2019.12_GfertPAR_modfit1.RData")
load("2019.12_GfertPAR_modfit1.RData")
```


```{r}
check.chains(out.2019D.G.fert.PAR.all)
```

Non-convergence observed for:
    - NECsigmoidal



Check if model median, credible intervals and NEC estimate are reasonable comPARed to the raw data
```{r}
plot(out.2019D.G.fert.PAR.all, all_models = TRUE, add.NEC = TRUE)
```
Based on graphical evaluation of model fit the following should be excluded:
    - ECxLinear
    

```{r}
plot(out.2019D.G.fert.PAR.all, add.EC10 = FALSE, add.NEC = FALSE)
```


Drop inappropriate models and models with non-convergence   
```{r}
out.2019D.G.fert.PAR.mod <- modify_jagsMANEC(out.2019D.G.fert.PAR.all, drop.models = c("NECsigmoidal", "ECxLinear"))
```

```{r}
plot(out.2019D.G.fert.PAR.mod, add.EC10 = FALSE, add.NEC = FALSE)
```

```{r}
plot(out.2019D.G.fert.PAR.mod, all_models = TRUE, add.NEC = TRUE)
```


Check for evidence of overdispersion for remaining models
```{r}
out.2019D.G.fert.PAR.mod$mod.stats
```

All candidate models had overdispersion parameters = 1.


Re-fit MANEC with over.disp = TRUE
```{r}
out.2019D.G.fert.PAR.all.od <- fit.jagsMANEC(data = data.2019D.G.fert.PAR, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 20000,
                        over.disp = TRUE)
beep("mario")
save(out.2019D.G.fert.PAR.all.od, file = "2019.12_GfertPAR_modfit3.RData")
load("2019.12_GfertPAR_modfit3.RData")
```

```{r}
check.chains(out.2019D.G.fert.PAR.all.od)
```
Minor indications of poor chain mixing or autocorrelation observed for:
    - ECxWeibull1 (beta)
    - NEC4param

Non-convergence observed for:
    - NECsigmoidal
    
  
Check if model median, credible intervals and NEC estimates are reasonable compared to the raw data
```{r}
plot(out.2019D.G.fert.PAR.all.od, all_models = TRUE, add.NEC = TRUE)
```

Based on graphical evaluation of model fit the following models should be excluded:
    - ECxLinear
    
    
Drop poor model fits and models with convergence or autocorrelation issues
```{r}
out.2019D.G.fert.PAR.mod.od <- modify_jagsMANEC(out.2019D.G.fert.PAR.all.od, drop.models = c("NECsigmoidal", "ECxLinear"))
```

```{r}
plot(out.2019D.G.fert.PAR.mod.od, all_models = TRUE, add.NEC = FALSE)
```


```{r}
plot(out.2019D.G.fert.PAR.mod.od, add.EC10 = TRUE, add.NEC = FALSE)
```

Compare to MANEC fitted using the binomial distribution
```{r}
plot(out.2019D.G.fert.PAR.mod, add.EC10 = TRUE, add.NEC = FALSE)
```





Rename model output for selected model
```{r}
out.2019D.G.fert.PAR <- out.2019D.G.fert.PAR.mod.od
```


```{r}
out.2019D.G.fert.PAR.NEC <- modify_jagsMANEC(out.2019D.G.fert.PAR, drop.models = c("ECx4param", "ECxWeibull1", "ECxWeibull2"))
```




Save the output for the selected model
```{r}
save(out.2019D.G.fert.PAR, file = "2019.12_GfertPAR_modfit.RData")
load("2019.12_GfertPAR_modfit.RData")
```

```{r}
save(out.2019D.G.fert.PAR.NEC, file = "2019.12_GfertPAR_modfit_NEC.RData")
load("2019.12_GfertPAR_modfit_NEC.RData")
```




##### Extract results

Extract NEC, EC10 and EC50 (with 95% credible intervals) from posterior and backtransform if required

```{r}
NEC.2019D.G.fert.PAR <- out.2019D.G.fert.PAR.NEC$NEC
NEC.2019D.G.fert.PAR <- 10^NEC.2019D.G.fert.PAR
NEC.2019D.G.fert.PAR
```


```{r}
EC10.2019D.G.fert.PAR <- extract_ECx(out.2019D.G.fert.PAR, ECx.val = 10, type = "absolute")
EC10.2019D.G.fert.PAR <- 10^EC10.2019D.G.fert.PAR
EC10.2019D.G.fert.PAR
```

```{r}
EC50.2019D.G.fert.PAR <- extract_ECx(out.2019D.G.fert.PAR, ECx.val = 50, type = "absolute")
EC50.2019D.G.fert.PAR <- 10^EC50.2019D.G.fert.PAR
EC50.2019D.G.fert.PAR
```




Extract complete posteriors for use in plotting and comparisons between light treatments
```{r}
pred.2019D.G.fert.PAR <- out.2019D.G.fert.PAR$pred.vals
str(pred.2019D.G.fert.PAR)
save(pred.2019D.G.fert.PAR, file = "2019.12_GfertPAR_predvals.RData")
load("2019.12_GfertPAR_predvals.RData")
```

```{r}
pred.2019D.G.fert.PAR.NEC <- out.2019D.G.fert.PAR.NEC$pred.vals
str(pred.2019D.G.fert.PAR.NEC)
save(pred.2019D.G.fert.PAR.NEC, file = "2019.12_GfertPARNEC_predvals.RData")
load("2019.12_GfertPARNEC_predvals.RData")
```



#### +UV/UV

##### Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
unique(data.2019D.G.fert.UV$raw.x)
par(mfrow=c(2,1))
hist(data.2019D.G.fert.UV$raw.x)
hist(data.2019D.G.fert.UV$suc/data.2019D.G.fert.UV$tot)
```



##### Fit models

Fit a model-averaged NEC model
```{r}
out.2019D.G.fert.UV.all <- fit.jagsMANEC(data = data.2019D.G.fert.UV, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 10000)
save(out.2019D.G.fert.UV.all, file = "2019.12_GfertUV_modfits1.RData")
load("2019.12_GfertUV_modfits1.RData")
beep("mario")
```


Check chain mixing and aurocorrelation for each model fit
```{r}
check.chains(out.2019D.G.fert.UV.all)
```

Indications of poor chain mixing and autocorrelation observed for several of the models fitted. 




Re-fit with higher burn-in and iterations
```{r}
out.2019D.G.fert.UV.all <- fit.jagsMANEC(data = data.2019D.G.fert.UV, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 20000)
save(out.2019D.G.fert.UV.all, file = "2019.12_GfertUV_modfits2.RData")
load("2019.12_GfertUV_modfits2.RData")
beep("mario")
```

```{r}
check.chains(out.2019D.G.fert.UV.all)
```
    
Minor indications of por chain mixing or autocorrelation observed for:
    - ECxWeibull1 (beta & EC50)
    - ECx4param (beta)
    - NEC4param (beta & SS)
    - NEC3param (SSsim & SS)


Poor chain mixing, autocorrelation or some non-convergence observed for:
    - NECsigmoidal (NEC, SS & SSsim)
    - NECHormesis (SS & SSsim)
    
Non-convergence observed for:
    - ECxWeibull2
    


```{r}
plot(out.2019D.G.fert.UV.all, add.EC10 = TRUE, add.NEC = FALSE)
```





Check if model median, credible intervals and NEC estimates are reasonable compared to the raw data
```{r}
plot(out.2019D.G.fert.UV.all, all_models = TRUE, add.NEC = TRUE)
```

Based on visual evaluation of model fit the following should be excluded:
    - ECxLinear


Remove models where chains did not converge or that do not make sense graphically
```{r}
out.2019D.G.fert.UV.mod <- modify_jagsMANEC(out.2019D.G.fert.UV.all, drop.models = c("NECHormesis", "NECsigmoidal", "ECxLinear", "ECxWeibull2"))
```

```{r}
plot(out.2019D.G.fert.UV.mod, add.NEC = TRUE, add.EC10 = TRUE)
```


Check for evidence of overdispersion
```{r}
out.2019D.G.fert.UV.mod$mod.stats
```

Overdispersion parameters < 1 for all candidate models. 




Fit a MANEC with over.disp=TRUE
```{r}
out.2019D.G.fert.UV.all.od <- fit.jagsMANEC(data = data.2019D.G.fert.UV, 
                        x.var = "log.x", 
                        y.var = "suc", 
                        trials.var = "tot",
                        model.set = "all",
                        burnin = 20000,
                        over.disp = TRUE)
save(out.2019D.G.fert.UV.all.od, file = "2019.12_GfertUV_modfits3.RData")
load("2019.12_GfertUV_modfits3.RData")
beep("mario")
```


```{r}
check.chains(out.2019D.G.fert.UV.all.od)
```

Some minor indications of poor chain mixing and/or autocorrelation observed for:
    - ECxWeibull1 (beta)
    - ECx4param
    - NEC4param (beta, NEC & bot)
    - NEC3param (NEC & SSsim)
    
    
Poor chain mixing or autocorrelation observed for:
    - ECxWeibull2 (beta & EC50)
    
    
Non-convergence observed for:
    - NECsigmoidal   


```{r}
plot(out.2019D.G.fert.UV.all.od, all_models = TRUE, add.NEC = TRUE)
```

Based on graphical evaluation of model fit all models except the following should be excluded:
    - NECHormesis
    - ECxLinear



```{r}
out.2019D.G.fert.UV.mod.od <- modify_jagsMANEC(out.2019D.G.fert.UV.all.od, drop.models = c("NECsigmoidal", "NECHormesis", "ECxLinear", "ECxWeibull2"))
```

```{r}
plot(out.2019D.G.fert.UV.mod.od, all_models = TRUE, add.NEC = TRUE)
```


```{r}
plot(out.2019D.G.fert.UV.mod.od, add.NEC = FALSE, add.EC10 = TRUE)
```

Compare to MANEC fitted using the binomial distribution
```{r}
plot(out.2019D.G.fert.UV.mod, add.NEC = FALSE, add.EC10 = TRUE)
```




Rename model output for selected model
```{r}
out.2019D.G.fert.UV <- out.2019D.G.fert.UV.mod.od
```


```{r}
out.2019D.G.fert.UV.NEC <- modify_jagsMANEC(out.2019D.G.fert.UV, drop.models = c("ECx4param", "ECxWeibull1"))
```



Save the output for the selected model
```{r}
save(out.2019D.G.fert.UV, file = "2019.12_GfertUV_modfit.RData")
load("2019.12_GfertUV_modfit.RData")
```

```{r}
save(out.2019D.G.fert.UV.NEC, file = "2019.12_GfertUV_modfitNEC.RData")
load("2019.12_GfertUV_modfitNEC.RData")
```




##### Extract results

Extract NEC, EC10 and EC50 (with 95% credible intervals) from posterior and backtransform if required


```{r}
NEC.2019D.G.fert.UV <- out.2019D.G.fert.UV.NEC$NEC
NEC.2019D.G.fert.UV <- 10^NEC.2019D.G.fert.UV
NEC.2019D.G.fert.UV
```


```{r}
EC10.2019D.G.fert.UV <- extract_ECx(out.2019D.G.fert.UV, ECx.val = 10, type = "absolute")
EC10.2019D.G.fert.UV <- 10^EC10.2019D.G.fert.UV
EC10.2019D.G.fert.UV
```


```{r}
EC50.2019D.G.fert.UV <- extract_ECx(out.2019D.G.fert.UV, ECx.val = 50, type = "absolute")
EC50.2019D.G.fert.UV <- 10^EC50.2019D.G.fert.UV
EC50.2019D.G.fert.UV
```



Extract complete posteriors for use in plotting and model comparison
```{r}
pred.2019D.G.fert.UV <- out.2019D.G.fert.UV$pred.vals
str(pred.2019D.G.fert.UV)
save(pred.2019D.G.fert.UV, file = "2019.12_GfertUV_predvals.RData")
load("2019.12_GfertUV_predvals.RData")
```


```{r}
pred.2019D.G.fert.UV.NEC <- out.2019D.G.fert.UV.NEC$pred.vals
str(pred.2019D.G.fert.UV.NEC)
save(pred.2019D.G.fert.UV.NEC, file = "2019.12_GfertUVNEC_predvals.RData")
load("2019.12_GfertUVNEC_predvals.RData")
```


#### PLot results

```{r}
library(ggplot2)
library(scales)
```



##### Combined "all models subset" plot

```{r}
p0= ggplot()
p0= p0+ scale_color_manual(values = c("Dark" = "slategrey", "PAR" = "seagreen", "UV" = "steelblue")) + theme_light()
#Add 95% credible intervals
p0= p0+  geom_ribbon(aes(x=10^pred.2019D.G.fert.Dark$x, ymin=pred.2019D.G.fert.Dark$lw, ymax=pred.2019D.G.fert.Dark$up, fill="slategrey"),  alpha=0.3) # try HEX code: #999999 or #666666
p0= p0+  geom_ribbon(aes(x=10^pred.2019D.G.fert.PAR$x, ymin=pred.2019D.G.fert.PAR$lw, ymax=pred.2019D.G.fert.PAR$up, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
p0= p0+  geom_ribbon(aes(x=10^pred.2019D.G.fert.UV$x, ymin=pred.2019D.G.fert.UV$lw, ymax=pred.2019D.G.fert.UV$up,fill="steelblue"),  alpha=0.3)
#Add model median
p0= p0+ geom_line(aes(x=10^pred.2019D.G.fert.Dark$x, y=pred.2019D.G.fert.Dark$y), color = 'grey30', size=0.5)
p0= p0+ geom_line(aes(x=10^pred.2019D.G.fert.PAR$x, y=pred.2019D.G.fert.PAR$y), color = 'grey30', size=0.5)
p0= p0+ geom_line(aes(x=10^pred.2019D.G.fert.UV$x, y=pred.2019D.G.fert.UV$y), color = 'grey30', size=0.5)
#Add raw data points
p0= p0+ geom_point(data = data.2019D.G.fert.Dark.raw, aes(x = raw.x, y = prop, colour=factor(factor), alpha = 0.3), size = data.2019D.G.fert.Dark.raw$tot*0.02, position=position_jitter(width = .025, height=0.02))
p0= p0+ geom_point(data = data.2019D.G.fert.PAR.raw, aes(x = raw.x, y = prop, colour=factor(factor), alpha = 0.3), size = data.2019D.G.fert.PAR.raw$tot*0.02, position=position_jitter(width = .025, height=0.02))
p0= p0+ geom_point(data = data.2019D.G.fert.UV.raw, aes(x = raw.x, y = prop, colour=factor(factor), alpha = 0.3), size = data.2019D.G.fert.UV.raw$tot*0.02, position=position_jitter(width = .025, height=0.02))
#Adjust axes, labeling etc
p0 = p0+ labs(x=expression(),
              y=expression(Fertilisation~success~("%")),
              subtitle = "a)") #x=expression(Concentration~(μg~TAH~"L"^{-1})),
p0= p0+ scale_y_continuous( limits = c(-0.03, 1.25), breaks = c(0, 0.25, 0.5, 0.75, 1.0, 1.25), labels = c(0, 25, 50, 75, 100, 125)) 
p0= p0+ scale_x_continuous(limits = c(0.018, 1000), trans="log10", breaks = c(0.02, 1, 10, 100, 1000), labels = c(0, 1, 10, 100, 1000))
p0= p0+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p0= p0+ scale_fill_manual(values = c("seagreen", "slategrey", "steelblue")) #try changing the order of these around until the right band has the right colour!
p0= p0+ theme(legend.position="none")
# p0 = p0  + theme(legend.position = c(0.9, 0.9))
p0
```

```{r}
Dec2019.GfertModfitplot <- p0
save(Dec2019.GfertModfitplot, file = "2019.12_Gfertmodfitplot.RData")
```



##### Combined "NEC subset" plot

```{r}
p0= ggplot()
p0= p0+ scale_color_manual(values = c("UV" = "steelblue", "PAR" = "seagreen", "Dark" = "slategrey")) + theme_light()
#Add 95% credible intervals
p0= p0+  geom_ribbon(aes(x=10^pred.2019D.G.fert.Dark.NEC$x, ymin=pred.2019D.G.fert.Dark.NEC$lw, ymax=pred.2019D.G.fert.Dark.NEC$up, fill="slategrey"),  alpha=0.3)
p0= p0+  geom_ribbon(aes(x=10^pred.2019D.G.fert.PAR.NEC$x, ymin=pred.2019D.G.fert.PAR.NEC$lw, ymax=pred.2019D.G.fert.PAR.NEC$up, fill="seagreen"),  alpha=0.3)
p0= p0+  geom_ribbon(aes(x=10^pred.2019D.G.fert.UV.NEC$x, ymin=pred.2019D.G.fert.UV.NEC$lw, ymax=pred.2019D.G.fert.UV.NEC$up,fill="steelblue"),  alpha=0.3)
#Add model median
p0= p0+ geom_line(aes(x=10^pred.2019D.G.fert.Dark.NEC$x, y=pred.2019D.G.fert.Dark.NEC$y), color = 'grey30', size=0.5)
p0= p0+ geom_line(aes(x=10^pred.2019D.G.fert.PAR.NEC$x, y=pred.2019D.G.fert.PAR.NEC$y), color = 'grey30', size=0.5)
p0= p0+ geom_line(aes(x=10^pred.2019D.G.fert.UV.NEC$x, y=pred.2019D.G.fert.UV.NEC$y), color = 'grey30', size=0.5)
#Add raw data points
p0= p0+ geom_point(data = data.2019D.G.fert.Dark.raw, aes(x = raw.x, y = prop, colour=factor(factor), alpha = 0.3), size = data.2019D.G.fert.Dark.raw$tot*0.015, position=position_jitter(width = .025, height=0.02))
p0= p0+ geom_point(data = data.2019D.G.fert.PAR.raw, aes(x = raw.x, y = prop, colour=factor(factor), alpha = 0.3), size = data.2019D.G.fert.PAR.raw$tot*0.015, position=position_jitter(width = .025, height=0.02))
p0= p0+ geom_point(data = data.2019D.G.fert.UV.raw, aes(x = raw.x, y = prop, colour=factor(factor), alpha = 0.3), size = data.2019D.G.fert.UV.raw$tot*0.015, position=position_jitter(width = .025, height=0.02))
#Adjust axes, labeling etc
p0 = p0+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})),
              y=expression(Fertilisation~success~("%")),
              subtitle = "a)")
p0= p0+ scale_y_continuous( limits = c(-0.03, 1.03), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p0= p0+ scale_x_continuous(limits = c(0.018, 1000), trans="log10", breaks = c(0.02, 1, 10, 100, 1000), labels = c(0, 1, 10, 100, 1000))
p0= p0+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p0= p0+ scale_fill_manual(values = c("seagreen", "slategrey", "steelblue")) #try changing the order of these around until the right band has the right colour!
p0= p0+ theme(legend.position="none")
# p0 = p0  + theme(legend.position = c(0.9, 0.9))
#p0= p0+ facet_wrap(~factor, nrow = 1)
p0
```


Rename and save plot
```{r}
Dec2019.GfertNECfitplot <- p0
save(Dec2019.GfertNECfitplot, file = "2019.12_GfertNECfitplot.RData")
```



#### Compare +/-UV posteriors

Ensure dependency packages are loaded
```{r}
library(dplyr)
library(tidybayes)
library(jagsNEC) #for manual function use
library(R2jags) #for manual function use
library(ggplot2)
```


##### NEC

Perform comparison of posterior distributions for survival NEC

Compare Dark to UV
```{r}
comp.2019D.G.fert.NEC.DarkvUV <- compare_posterior(out.2019D.G.fert.Dark, out.2019D.G.fert.UV.NEC, comparison = "NEC") #1st model=blue, 2nd model=orange; #place Dark model first and UV model second for colour matching in custom plots
comp.2019D.G.fert.NEC.DarkvUV
```

Filter posterior density based on light treatment
```{r}
comp.2019D.G.fert.NEC.Dark <- filter(comp.2019D.G.fert.NEC.DarkvUV$df3.s, curve=="blue")
comp.2019D.G.fert.NEC.UV <- filter(comp.2019D.G.fert.NEC.DarkvUV$df3.s, curve=="orange")
```



Compare Dark to PAR
```{r}
comp.2019D.G.fert.NEC.DarkvPAR <- compare_posterior(out.2019D.G.fert.Dark, out.2019D.G.fert.PAR.NEC, comparison = "NEC") #1st model=blue, 2nd model=orange; #place Dark model first and UV model second for colour matching in custom plots
comp.2019D.G.fert.NEC.DarkvPAR
```

Filter posterior density based on light treatment
```{r}
comp.2019D.G.fert.NEC.PAR <- filter(comp.2019D.G.fert.NEC.DarkvPAR$df3.s, curve=="orange")
```



Add a new variable defining the light treatment
```{r}
comp.2019D.G.fert.NEC.Dark <- mutate(comp.2019D.G.fert.NEC.Dark, factor = "Dark") 
comp.2019D.G.fert.NEC.PAR <- mutate(comp.2019D.G.fert.NEC.PAR, factor = "PAR")
comp.2019D.G.fert.NEC.UV <- mutate(comp.2019D.G.fert.NEC.UV, factor = "UV")
```


Combine the posterior density outputs into one data frame:
```{r}
comp.2019D.G.fert.NEC.comb <- rbind(comp.2019D.G.fert.NEC.Dark, comp.2019D.G.fert.NEC.PAR, comp.2019D.G.fert.NEC.UV)
```




For custom plotting of survival NEC comparison
```{r}
p1 = ggplot(comp.2019D.G.fert.NEC.comb, aes(x=PS))+geom_density(aes(group=factor, color=factor , fill=factor), alpha=0.4) #df3.s is an object returned by compare_posterior()
p1 = p1 + stat_pointinterval(aes(y = 0.00, x = PS, group=factor),.width = c(.66, .95), size=0.5)+
  theme_light()
p1 = p1+scale_fill_manual( values = c("slategrey", "seagreen", "steelblue"))+
  scale_color_manual( values = c("grey","grey", "grey","gery", "grey","grey", "grey","grey"))+theme(legend.position="none")
p1 = p1 + scale_y_continuous(limits = c(-0.5, 20), name ="Posterior probability density") 
p1 = p1 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p1 = p1 + scale_x_continuous(limits = c(-0.6, 3.3), breaks = c(0, 1, 2, 3), labels = c(1, 10, 100, 1000)) 
p1 = p1 + labs(x=expression(Threshold~concentration~(μg~TAH~"L"^{-1})), 
               subtitle = "b)") #x=expression(Threshold concentration~(μg~TAH~"L"^{-1})))
p1= p1+ annotate("text", label = expression(1.2*"10"^{6}~sperm~"ml"^{-1}), x = 0.01, y = 19.7, size = 2.6, colour = "grey20")
p1= p1+ annotate("text", label = expression(Probability~of~NEC~difference), x = 0.55, y = 16, size = 2.8, colour = "grey20") #0.85 of the max y-axis limit
p1= p1+ annotate("text", label = "UV < Dark = 100%", x = 0.55, y = 14.5, size = 2.4, colour = "grey20") #0.906 of first annotation
p1= p1+ annotate("text", label = "PAR < Dark = 96%", x = 0.55, y = 13.2, size = 2.4, colour = "grey20")
p1
```

Rename and save plot
```{r}
Dec2019.GfertNECcomp <- p1
save(Dec2019.GfertNECcomp, file = "2019.12_GfertNECcomp.RData")
```



##### EC50

As no EC50 could be derived for the Dark light treatment it was not included in the below posterior density comparison.


Perform comparison of posterior distributions for PAR and UV fertilisation EC50
```{r}
comp.2019D.G.fert.EC50.PARvUV <- compare_posterior(out.2019D.G.fert.PAR, out.2019D.G.fert.UV, comparison="ECx", ECx.val = 50) #place PAR model first and UV model second for colour matching in custom plots
comp.2019D.G.fert.EC50.PARvUV
```

Filter posterior density based on light treatment
```{r}
comp.2019D.G.fert.EC50.PAR <- filter(comp.2019D.G.fert.EC50.PARvUV$df3.s, curve=="blue")
comp.2019D.G.fert.EC50.UV <- filter(comp.2019D.G.fert.EC50.PARvUV$df3.s, curve=="orange")
```




Add a new variable defining the light treatment
```{r}
comp.2019D.G.fert.EC50.PAR <- mutate(comp.2019D.G.fert.EC50.PAR, factor = "PAR")
comp.2019D.G.fert.EC50.UV <- mutate(comp.2019D.G.fert.EC50.UV, factor = "UV")
```


Combine the posterior density outputs into one data frame:
```{r}
comp.2019D.G.fert.EC50.comb <- rbind(comp.2019D.G.fert.EC50.PAR, comp.2019D.G.fert.EC50.UV)
```



For custom plotting of EC50 comparison
```{r}
p1 = ggplot(comp.2019D.G.fert.EC50.comb, aes(x=PS))+geom_density(aes(group=factor, color=factor , fill=factor), alpha=0.4) #df3.s is an object returned by compare_posterior()
p1 = p1 + stat_pointinterval(aes(y = 0.00, x = PS, group=factor),.width = c(.66, .95), size=0.5)+
  theme_light()
p1 = p1+scale_fill_manual( values = c("seagreen", "steelblue"))+
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p1 = p1 + scale_y_continuous(limits = c(-0.5, 20.5), name ="Posterior probability density") 
p1 = p1 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p1 = p1 + scale_x_continuous(limits = c(-0.6, 3.3), breaks = c(0, 1, 2, 3), labels = c(1, 10, 100, 1000)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p1 = p1 + labs(x=expression(Threshold~concentration~(μg~TAH~"L"^{-1})), 
               subtitle = "b)") #EC[50]~(μg~TAH~"L"^{-1})))
#p1= p1+ annotate("text", label = "b.  (EC50)", x = -0.7, y = 19, size = 4.6)
p1= p1+ annotate("text", label = expression(1.2*"10"^{6}~sperm~"ml"^{-1}), x = 0.01, y = 20, size = 2.6, colour = "grey20")
p1= p1+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 17, size = 2.8, colour = "grey20") #0.85 of the max y-axis limit
p1= p1+ annotate("text", label = "UV < PAR = 100%", x = 0.55, y = 15.5, size = 2.4, colour = "grey20") #0.906 of first annotation
p1
```

```{r}
Dec2019.GfertEC50comp <- p1
save(Dec2019.GfertEC50comp, file = "2019.12_GfertEC50comp.RData")
```



### Create layouts and export

```{r}
#devtools::install_github("kassambara/ggpubr")
library(ggpubr)
```


Create layout

Load graphics
```{r}
load("2019.12_Gfertmodfitplot.RData") #Dec2019.GfertModfitplot
load("2019.12_GfertEC50comp.RData") #Dec2019.GfertEC50comp
load("2019.12_GfertNECfitplot.RData") #Dec2019.GfertNECfitplot
load("2019.12_GfertNECcomp.RData") #Dec2019.GfertNECcomp
```


```{r}
layout.E.surv <- ggarrange(Dec2019.GfertModfitplot, Dec2019.GfertEC50comp, Dec2019.GfertNECfitplot, Dec2019.GfertNECcomp,
          ncol = 2, nrow = 2,
          widths = c(0.5, 0.5))
layout.E.surv
```



Export layout
```{r}
pdf("test3b.pdf", width = 8.27, height = 4.92) #height and width in inches
layout.E.surv
dev.off()
```



